Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-10 doc/icml-presentation/presentation.tex

  \begin{centering}
  \begin{tikzpicture}
    % Tasks.
    \node[style=box] (gen) at (0,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/gen.png}\\
      \hfill Generative Models
      }};

    \node<1->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<2->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<2->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Logistic Regression
        \item Conditional Random Fields
        \item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
  \end{centering}

@@

\begin{frame}
  \frametitle{Spectral Methods}
  \begin{itemize}
     \item Representation Learning
    \begin{itemize}
    \item Subspace identification [Ljung, 1987]
    \item Observable operator models [Jaeger, 2000]
    \item {\bf Hidden Markov models [Hsu et al, 2009]}
    \item Low-treewidth graphs [Parikh et al., 2012]
    \item Weighted finite state automata [Balle \& Mohri, 2012]
  \end{itemize}
     \item<2-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
  \note[item]{\todo{Talk about observable operator stuff.}}
\end{frame}

\begin{frame}
  \frametitle{Spectral Methods via Tensor Factorization}
  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1>[style=box] (moments) at (0,0) {\objw{12cm}{%
      \begin{align*}
        %\underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
        %\underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
        \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1>[style=box,below=0.4cm of moments] {\objw{12cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2>[style=box] (tensorf) at (0,0) {\objw{12cm}{%
      Given orthonormal $\beta_h$,
          \begin{align*}
            M_3(\beta_h,\beta_h) 
              %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
              %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
              &= \pi_{h'} \beta_{h}.
          \end{align*}
      }};

    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
      \hfill {Tensor Power Method}
      }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node<1-9>[style=box] at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    {\bf Parameters:} $\pi = [\pi_1, \cdots, \pi_k]$ and $B = [ \beta_1 | \cdots | \beta_k ]$.
    For a given $x$,
      \begin{itemize}
        \item<2-> $h \in [k] \sim Mult(\pi)$.
        \item<3-> $\epsilon \sim \mathcal{E}$.
        \item<4-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};
    \node<10>[style=box] at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc-model.png}\\
    {\bf Given:} $\mathcal{D} = (x_i, y_i)_{i=1}^{n}$,\\
    can we {\bf estimate parameters} $\pi$ and $B = [ \beta_1 | \cdots | \beta_k ]$?
      }};

    %\node<2-> at (6,0) {Discriminative Models};
    \node[style=box] at (6,0) {\obj{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-2.png}
    \includegraphics<2-3>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3a.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3b.png}
    \includegraphics<5>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4a.png}
    \includegraphics<6-7>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4b.png}
    \includegraphics<8>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4c.png}
    \includegraphics<9>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-5.png}
    \includegraphics<10>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-6.png}
      \\{\em Data}
      }};
  \end{tikzpicture}
  \end{centering}

  \note[item]{First step, consider a simple discriminative model, mixture of linear regressions.}
  \note[item]{The mixture of linear regressions model defines a conditional distribution over a response $y \in \Re$ given covariates $x \in \Re^d$.}
     \note[item]{The generative procedure is as follows,
       \begin{enumerate}
        \item Draw a mixture component $h \in [k] \sim Mult(\pi)$, where $\pi = [\pi_1 | \dots | \pi_k]$ defines the mixture proportions.
        \item Draw the noise $\epsilon \sim \mathcal{E}$, where $\mathcal{E}$ is the noise distribution.
        \item Set $y = \beta_h^T x + \epsilon$, where $\{\beta_h\}_{h=1}^{k}$ are the conditional means of the regression coefficients.
      \end{enumerate}}
   \note[item]{The parameters that we would like to learn from this model are $\pi$ and $B = [ \beta_1 | \cdots | \beta_k ]$.}
\end{frame}

% \begin{frame}
%   \frametitle{Method of Moments for Generative LVMs.}
% 
%   \begin{centering}
%   \begin{tikzpicture}
%     % x, y
%     \node<1->[style=box]  (moments) at (0,0) {\objw{12cm}{%
%       \begin{align*}
%         \underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
%         \underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
%         \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
%       \end{align*}
%     }};
%     \node<1>[style=box,below=0.1cm of moments] {\objw{12cm}{%
%     \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/moments.png}
%       }};
%     \node<2->[style=box,below=0.1cm of moments] {\objw{12cm}{%
%       \begin{itemize}
%         \item<2-> {\bf Tensor Power Method} for orthonormal $\beta_h$,
%           \begin{align*}
%             M_3(\beta_h,\beta_h) 
%               &= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
%               &= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
%               &= \pi_{h'} \beta_{h}.
%           \end{align*}
%         \item<3-> Use $M_2$ to whiten $M_3$.
%       \end{itemize}
%       }};
%   \end{tikzpicture}
%   \end{centering}
% 
%     \note[item]{\bf We can recover the means of a generative LVM by exploiting their symmetric structure.}
%     \note[item]{\begin{align*} M_2 &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & M_3 &= \sum_{h=1}^k \pi_h \beta_h\tp{3}.  \end{align*}}
%       \note[item]{In general, $M_2$ is insufficient to identify the model, because it is invariant to rotations of $B$. }
%       \note[item]{If the $\beta_h$ were orthogonal, then the eigenvectors and eigenvalues of $M_3$ would give us the answer. }
%       \note[item]{In general, we need both $M_2$ and $M_3$. We can use the whitening transformation for $M_2$ to whiten $M_3$ such that it has a orthogonal decomposition.}
%       \note[item]{The robust tensor power method by \cite{AnandkumarHsuGe2012} find stable eigenvectors.}
% \end{frame}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
          y &= \underbrace{\beta_h^T}_{\textrm{random}} x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{\E[\beta_h]^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - M_1)^T x + \epsilon}_{\textrm{noise}} \\
          }
        \end{align*}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}
  \end{centering}

    \note[item]{The powers of the response variables $y^p$ are linear measurements of the moments of the parameters $M_p$!}
    \note[item]{As noted earlier, the first problem we run into is that we can't observe the moments of the parameters $B$ and $\pi$ directly!}
    \note[item]{However, observe that 
    \begin{align}
      y &= \innerp{\beta_h}{x} + \epsilon \\
        &= \innerp{M_1}{x} + \underbrace{{\beta_h - M_1}{x} + \epsilon }_{\textrm{noise}},
    \end{align}
    where $M_1 = \sum_{h=1}^k \pi_h \beta_h$, the mean regression coefficient.}
    \note[item]{We note that while the noise term is dependent on $x$, it has a zero-mean. Thus, we could potentially recover $M_1$ through regression.}
    \note[item]{Similarly, we can cast the remaining two terms as regression problems.}
    \note[item]{An additional fact that we can exploit is that both $M_2$ and $M_3$ are low rank, so we can use low-rank regression to recover estimates $\hat M_2$ and $\hat M_3$ efficiently from data.}
\end{frame}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{%
            y &= \underbrace{M_1^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - M_1)^T x + \epsilon}_{\textrm{noise}} \\
            M_1 &= \E[\beta_h] \\
          }
          \action<+->{%
            y^2 
              %&= (\beta_h^T x)^2 + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              %&= \trace(\beta_h\tp{2} x\tp{2}) + 2 (\beta_h^T x) \epsilon + \epsilon^2 \\
              %&= \trace(M_2 x\tp{2}) + \E[\epsilon^2] + \trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon \\
              &= \trace(M_2 x\tp{2}) + \underbrace{\E[\epsilon^2]}_{\textrm{bias}} + \underbrace{\trace((\beta_h\tp{2} - M_2) x\tp{2}) + 2 (\beta_h^T x) \epsilon}_{\textrm{noise}} \\
              M_2 &= \E[\beta_h\tp{2}] \\
          }
          \action<+->{%
          y^3 &= \innerp{M_3}{x\tp{3}} + \textrm{bias} + \textrm{noise} \\
          \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk}.
          }
        \end{align*}
      }};
    \node<4->[style=box,below=0.1cm of measurements]  {\objw{12cm}{%
    We can use \uncover<5->{{\color{blue}{(low-rank)}}} regression to recover $M_p$ from linear measurements.\\
    \uncover<5->{\hfill {\color{blue}{{[Negabhan and Wainwright (2009); Tomioka (2011)]}}}}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}
  \end{centering}

    \note[item]{The powers of the response variables $y^p$ are linear measurements of the moments of the parameters $M_p$!}
    \note[item]{As noted earlier, the first problem we run into is that we can't observe the moments of the parameters $B$ and $\pi$ directly!}
    \note[item]{However, observe that 
    \begin{align}
      y &= \innerp{\beta_h}{x} + \epsilon \\
        &= \innerp{M_1}{x} + \underbrace{{\beta_h - M_1}{x} + \epsilon }_{\textrm{noise}},
    \end{align}
    where $M_1 = \sum_{h=1}^k \pi_h \beta_h$, the mean regression coefficient.}
    \note[item]{We note that while the noise term is dependent on $x$, it has a zero-mean. Thus, we could potentially recover $M_1$ through regression.}
    \note[item]{Similarly, we can cast the remaining two terms as regression problems.}
    \note[item]{An additional fact that we can exploit is that both $M_2$ and $M_3$ are low rank, so we can use low-rank regression to recover estimates $\hat M_2$ and $\hat M_3$ efficiently from data.}
\end{frame}

% \begin{frame}
%   \frametitle{Method of Moments for the Mixture of Linear Regressions.}
% 
%   \begin{centering}
%   \begin{tikzpicture}
%     % x, y
%     \node[style=box] (note) at (0,0) {\objw{12cm}{%
%       {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
%       }};
%     \node[style=box,below=0.1cm of note] {\objw{12cm}{%
%       \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-1.png}
%       \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-2.png}
%       \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-3.png}
%       }};
%   \end{tikzpicture}
%   \end{centering}
% \end{frame}

@@

  \begin{centering}
  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      %\includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-2.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-3.png}
      %\includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-4.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-5.png}
      }};
  \end{tikzpicture}
  \end{centering}

@@

  \begin{centering}
  \begin{tikzpicture}
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom1.png}
        \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
  \end{centering}

>>>>

  \begin{tikzpicture}
    % Tasks.
    \node[style=box] (gen) at (0,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/gen.png}\\
      \hfill Generative Models
      }};
    \node[scale=0.7] at (0.5,0.5) {Latent variable};

    \node<2->[style=box,below=0.1cm of gen] {\obj{%
      {\bf Generative Models}
      \begin{itemize}
        \item Gaussian Mixture Models
        \item Hidden Markov Models
        \item Latent Dirichlet Allocation
        \item PCFGs
        \item \dots
      \end{itemize}
      }};
    \node<3->[style=box] (disc) at (6,0) {\objw{6cm}{%
      \includegraphics[width=\textwidth,height=3cm,keepaspectratio]{figures/disc.png}\\
      \hfill Discriminative Models
      }};
    \node<4->[style=box,below=0.1cm of disc] (disc-models) {\obj{%
    {\bf Discriminative Models}
      \begin{itemize}
        \item Logistic Regression
        \item Latent CRFs
        \item Discriminative LDA
        %\item Semi-Latent Topic Models (Wang and Mori, 2009)
        %\item Discriminative Parsers (Liang et.\ al, 2006)
        \item \dots
      \end{itemize}
      }};
    \node<5->[style=box,below=0.1cm of disc-models] {\obj{%
      {\bf Easy to include features and tend to be more accurate.}
    }};

  \end{tikzpicture}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Method of Moments a.k.a.\ Spectral Methods}
  \begin{itemize}
    \item<+-> Method of Moments [Pearson, 1894]
    \item<+-> Observable operator models
    \begin{itemize}
      \item Subspace identification [Ljung, 1987]
      \item Observable operator models [Jaeger, 2000]
        \note[item]{Entry point into machine learning}
      \item {\bf Hidden Markov models [Hsu et al, 2009]}
        \note[item]{Entry point into machine learning}
      \item Low-treewidth graphs [Parikh et al., 2012]
      \item Weighted finite state automata [Balle \& Mohri, 2012]
    \end{itemize}
     \item<+-> Parameter Estimation
  \begin{itemize}
    \item Mixture of Gaussians [Kalai/Moitra/Valiant, 2010]
    \item {\bf Mixture models, HMMs [Anandkumar/Hsu/Kakade, 2012]}
    \item Latent Dirichlet Allocation [Anandkumar/Hsu/Kakade, 2012]
    \item Stochastic block models [Anandkumar/Ge/Hsu/Kakade, 2012]
    \item Linear Bayesian networks [Anandkumar/Hsu/Javanmard/Kakade, 2012]
  \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{itemize} 
      \item Generative process:
      \begin{align*}
        h \in [k] &\sim \Mult(\pi) \\
        x &\sim \normal{\beta_h}{\sigma^2}.
      \end{align*}
    \end{itemize}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<2->[style=box,below=0.1cm of defn] {\objw{6cm}{%
    \begin{itemize} 
      \item Moments:
    \begin{align*}
        \action<2->{%
        \E[x|h] &= \beta_h \\
        }
        \action<3->{%
        \E[x] &= \sum_h \pi_h \beta_h \\
        }
        \action<4->{%
        \E[x\tp{2}] &= \sum_h \pi_h \beta_h{\hlmath{\tp{2}}} \\
                    &= \sum_h \pi_h (\beta_h \beta_h^T) \\
                    }
        \action<5->{%
        \E[x\tp{3}] &= \sum_h \pi_h \beta_h\tp{3}.
        }
      \end{align*}
    \end{itemize}
    }};
    %\tikzrect{1}{1};
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{1}{1};
    \node at (7,-2.5) {$\E[x\tp{2}]$};
    \node at (4.5,-2.5) {$d$};
    }
    \uncover<5->{%
    \tikzcube{black,fill=white}{(6,-4,0)}{1}{1}{1};
    \node at (7,-4.5,0) {$\E[x\tp{3}]$};
    \node at (4.5,-4.5) {$d$};
    \node at (4.5,-4.5) {$d$};
    }
  \end{tikzpicture}

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (defn) at (0,0) {\objw{6cm}{%
    \begin{align*}
        \action<1->{%
        x\tp{3}_{ijk} &= x_i x_j x_k \comment{indexing}\\
        }
        \action<2->{%
        A \cdot B &= \sum_{ijk} A_{ijk} B_{ijk} \comment{inner product}\\
        }
        \action<3->{%
        A(u)_{ij} &= \sum_{k} A_{ijk} u_k \comment{projection}\\
        }
        \action<4->{%
        A(u,v)_{i} &= \sum_{jk} A_{ijk} u_j v_k \comment{projection} \\
        }
      \end{align*}
    }};
    \tikzcube{black,fill=white}{(6,2,0)}{1}{1}{1};
    \node (pt) at (5.75,1.75,0) {$\hlmath{\times}$};
    \uncover<3->{%
    \tikzrect{black,fill=white}{(6,0)}{1}{1};
    }
    \uncover<4->{%
    \tikzrect{black,fill=white}{(6,-2)}{0.1}{1};
    }
  \end{tikzpicture}

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \begin{tikzpicture}
    % x, y
    \node<1->[style=box] (moments) at (0,0) {\objw{6cm}{%
      Assume $\beta_h$ to be orthogonal;
      \begin{align*}
        \E[x\tp{3}] &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
      \end{align*}
    }};
    \node<1->[style=box] (models) at (6,0) {\objw{6cm}{%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/gen.png}
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    }};

    \node<1-> at (0,-3) {\objw{6cm}{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box] at (6,-3) {\objw{6cm}{%
      $\beta_h$ are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}

        \hfill{\em Anandkumar, Hsu, et.\ al (2012)}
      }};
%
%    \node<2>[style=box,below=0.1cm of tensorf] {\objw{12cm}{%
%    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor-decomp.png}
%      \hfill {Tensor Power Method}
%      }};
  \end{tikzpicture}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{4cm}{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc.png}
      \begin{itemize}
        \item<2-> $h \in [k] \sim \Mult(\pi)$.
        \item<4-> $y = \beta_h^T x + \epsilon$.
      \end{itemize}
      }};

    \node[style=box] at (6,0) {\obj{%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-2.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3a.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-3b.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4a.png}
    \includegraphics<5>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4b.png}
    %\includegraphics<6>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-4c.png}
    \includegraphics<6>[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-5.png}
      }};
  \end{tikzpicture}
\end{frame}

  \begin{tikzpicture}
    \node[style=box] (data) at (0,0) {\obj{%
    \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/mlr-data-6.png}
      \\{\em Data}
      }};

    % x, y
    \node[style=box] (params) at (7,0) {\objw{4cm}{%
    \includegraphics[width=\textwidth,height=4cm,keepaspectratio]{figures/disc.png}
    \\
    {\bf Parameters: $\pi, B$}
    }};

    \draw[->,dashed] (data) -- node[above]{?} (params);

  \end{tikzpicture}
\end{frame}

% \begin{frame}
%   \frametitle{Method of Moments for Generative LVMs.}
% 
%   \begin{tikzpicture}
%     % x, y
%     \node<1->[style=box]  (moments) at (0,0) {\objw{12cm}{%
%       \begin{align*}
%         \underbrace{\E[x]}_{M_1} &= \sum_{h=1}^k \pi_h \beta_h & 
%         \underbrace{\E[x\tp{2}]}_{M_2} &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & 
%         \underbrace{\E[x\tp{3}]}_{M_3} &= \sum_{h=1}^k \pi_h \beta_h\tp{3}. 
%       \end{align*}
%     }};
%     \node<1>[style=box,below=0.1cm of moments] {\objw{12cm}{%
%     \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/moments.png}
%       }};
%     \node<2->[style=box,below=0.1cm of moments] {\objw{12cm}{%
%       \begin{itemize}
%         \item<2-> {\bf Tensor Power Method} for orthonormal $\beta_h$,
%           \begin{align*}
%             M_3(\beta_h,\beta_h) 
%               &= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
%               &= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
%               &= \pi_{h'} \beta_{h}.
%           \end{align*}
%         \item<3-> Use $M_2$ to whiten $M_3$.
%       \end{itemize}
%       }};
%   \end{tikzpicture}
% 
%     \note[item]{\bf We can recover the means of a generative LVM by exploiting their symmetric structure.}
%     \note[item]{\begin{align*} M_2 &= \sum_{h=1}^k \pi_h \beta_h\tp{2} & M_3 &= \sum_{h=1}^k \pi_h \beta_h\tp{3}.  \end{align*}}
%       \note[item]{In general, $M_2$ is insufficient to identify the model, because it is invariant to rotations of $B$. }
%       \note[item]{If the $\beta_h$ were orthogonal, then the eigenvectors and eigenvalues of $M_3$ would give us the answer. }
%       \note[item]{In general, we need both $M_2$ and $M_3$. We can use the whitening transformation for $M_2$ to whiten $M_3$ such that it has a orthogonal decomposition.}
%       \note[item]{The robust tensor power method by \cite{AnandkumarHsuGe2012} find stable eigenvectors.}
% \end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{
          y &= \underbrace{\beta_h^T}_{\textrm{random}} x + \epsilon \\
          }
          \action<+->{
            &= \underbrace{\E[\beta_h]^T x}_{\textrm{linear measurement}} + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
        \end{align*}
      }};
    %\node[style=box] at (6,0) {\objw{8em}{%
    %  {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
    %  }};
  \end{tikzpicture}

    \note[item]{The powers of the response variables $y^p$ are linear measurements of the moments of the parameters $M_p$!}
    \note[item]{As noted earlier, the first problem we run into is that we can't observe the moments of the parameters $B$ and $\pi$ directly!}
    \note[item]{However, observe that 
    \begin{align}
      y &= \innerp{\beta_h}{x} + \epsilon \\
        &= \innerp{\E[\beta_h]}{x} + \underbrace{{\beta_h - \E[\beta_h]}{x} + \epsilon }_{\textrm{noise}},
    \end{align}
    where $M_1 = \sum_{h=1}^k \pi_h \beta_h$, the mean regression coefficient.}
    \note[item]{We note that while the noise term is dependent on $x$, it has a zero-mean. Thus, we could potentially recover $M_1$ through regression.}
    \note[item]{Similarly, we can cast the remaining two terms as regression problems.}
    \note[item]{An additional fact that we can exploit is that both $M_2$ and $M_3$ are low rank, so we can use low-rank regression to recover estimates $\hat M_2$ and $\hat M_3$ efficiently from data.}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
        \begin{align*}
          \action<+->{%
            y &= \underbrace{\E[\beta_h]^T \odot x}_{\textrm{linear measurement}} &\quad & + \underbrace{(\beta_h - \E[\beta_h])^T x + \epsilon}_{\textrm{noise}} \\
          }
          \action<+->{%
            y^2 
              &= \E[\beta_h\tp{2}] \odot x\tp{2} &+ \textrm{bias} &+ \textrm{noise} \\
          }
          \action<+->{%
          y^3 &= \E[\beta_h\tp{2}] \odot x\tp{3} &+ \textrm{bias} &+ \textrm{noise} \\
          }
        \end{align*}

        \uncover<4->{%
          We can use regression to recover $M_p$ from linear measurements.\\
          }
      }};
  \end{tikzpicture}
\end{frame}

  \begin{tikzpicture}
    % x, y
    \node[style=box] (measurements) at (0,0) {\objw{12cm}{%
      \includegraphics[width=\textwidth,height=6cm,keepaspectratio]{figures/tensor.png}
      }};
    \node<2->[style=box,below=0.1cm of measurements] {\objw{12cm}{%
      We can use low-rank regression techniques [Negabhan \& Wainwright 2009; Tomioka 2011].
      \begin{align*}
        \hat\E[\beta_h\tp{2}] &= \arg\min_{M} \left(y^2 - M] \odot x\tp{2}\right)^2_{(x,y)\in\mathcal{D}} + \|M\|_{*} \\
        \|M\|_{*} &= \sum_i \sigma_i(M).
      \end{align*}
      }};
  \end{tikzpicture}
\end{frame}

% \begin{frame}
%   \frametitle{Method of Moments for the Mixture of Linear Regressions.}
% 
%   \begin{tikzpicture}
%     % x, y
%     \node[style=box] (note) at (0,0) {\objw{12cm}{%
%       {$y^p$ are linear measurements of the moments of the parameters $M_p$!}
%       }};
%     \node[style=box,below=0.1cm of note] {\objw{12cm}{%
%       \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-1.png}
%       \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-2.png}
%       \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/regression-3.png}
%       }};
%   \end{tikzpicture}
% \end{frame}

\begin{frame}
  \frametitle{Overview: Spectral Experts}

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      }};
  \end{tikzpicture}
\end{frame}

@@

  \begin{tikzpicture}
    % x, y
    \node[style=box] at (0,0) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-1.png}
      %\includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-2.png}
      \includegraphics<2>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-3.png}
      %\includegraphics<4>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-4.png}
      \includegraphics<3>[width=\textwidth,height=8cm,keepaspectratio]{figures/err-5.png}
      }};
  \end{tikzpicture}

@@

  \begin{tikzpicture}
    \node[style=box] at (0,-1.5) {\objw{12cm}{%
      \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom-em1.png}
      \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom-em2.png}
        \hfill{\em expected log-likelihood}
      }};
  \end{tikzpicture}
